AHABus \& FCORE:\\Modular Bus for High-Altitude Balloon Missions

### 2017-04-08 chapters/04-results.tex
Better data parsing

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
mark repeat={5},
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]

>>>>

\begin{figure}[h]
\begin{tikzpicture}
\begin{axis} [
xlabel=Mission Elapsed Time (\SI{}{\second}),
ylabel=Received Data (\SI{}{\byte}),
mark size=1.0pt,
mark repeat={10},
legend style ={
    at={(0.02,0.95)}, 
    anchor=north west, draw=black, 
    fill=white,align=left
}
]
